linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-09-16 code/linguistic_analysis_C-D.Rmd
mattr instead of simple type token ratio

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
a<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==0), 0,5) + 
  ylab("Number of utterances")+  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank())+ labs(subtitle = "Block1")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
b<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==1), 6,11) +  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank())+ 
  labs(subtitle = "Block2")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
c<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==2), 12,17) +  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank())+ 
  labs(subtitle = "Block3")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
d<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==3), 18,23) +
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),axis.text.y = element_blank())+ 
  labs(subtitle = "Block4")

@@

@@

d_flowers_text_trial <- d_flowers %>%
    group_by(gameId, trialNum, condition) %>%
    mutate(text_block = paste0(text, collapse = " ")) %>%
    select(-c(text)) %>%
    distinct()

#t<-str_split(text_, " ", 1:6)
#y<- paste(unlist(lapply(t,head,n=5)), collapse=" ")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_ttr_trial, 
       aes(x=trialNum, y=ttr_,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.05) +
 # facet_grid(rows =vars(condition)) +
  xlab("Trial Number") + 
  ylab("Type to Token Ratio (TTR)") + 
  ylim(0,1)+
  scale_color_bay() + theme_jmank() +
  theme(legend.position = "bottom")
 # theme(text = element_text(size = 30))
#dev.off()

>>>>

a<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==0), 0,5) + 
  ylab("Number of utterances")+  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank())+ labs(subtitle = "Block1")

b<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==1), 6,11) +  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank())+ 
  labs(subtitle = "Block2")

c<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==2), 12,17) +  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank())+ 
  labs(subtitle = "Block3")

d<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==3), 18,23) +
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),axis.text.y = element_blank())+ 
  labs(subtitle = "Block4")

@@

library(koRpus)
install.koRpus.lang(lang=c("en"))
library(koRpus.lang.en)

MATTR <- function(txt, window=100, char=FALSE, ...){
  if(isTRUE(char)){
    char.value <- "MATTR"
  } else {
    char.value <- c()
  }
  results <- lex.div(txt=txt, window=window, measure="MATTR", char=char.value)
  return(results)
}

@@

ttrMATTR <- function(text_){
  text_ <- tolower(text_)
  total_words = sapply(strsplit(text_, " "), length)
  if (total_words >21){
  text_obj <- tokenize(text_, format="obj", lang="en")
  ttr_<- MATTR(text_obj, window=21)[1]
  return(ttr_)
  }
  else {
  ttr_<- 0
  }
}

d_flowers_text_trial <- d_flowers %>%
    group_by(gameId, trialNum, condition) %>%
    mutate(text_block = paste0(text, collapse = " ")) %>%
    #select(-c(text, time, playerId)) %>%
    select(gameId, trialNum, condition, text_block) %>%
    distinct()

d_flowers_ttr_trial <- d_flowers_text_trial %>%
  mutate(ttr_ = ttrMATTR(text_block))

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_ttr_trial, 
       aes(x=trialNum, y=ttr_,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.05) +
 # facet_grid(rows =vars(condition)) +
  xlab("Trial Number") + 
  ylab("Moving Average Type to Token Ratio (MATTR)") + 
  ylim(0,1)+
  scale_color_bay() + theme_jmank() +
  theme(legend.position = "bottom")
 # theme(text = element_text(size = 30))
#dev.off()
